Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-10 WSSSPE3/report/wg_appendix_funding_spec_expert.tex
a few more small changes

In addition to the points noted in the main discussion~\ref{RSE}, we also
discussed the following:

@@

However this area develops, the need for funding to secure software as a
cyberinfrastructure component is clear. Funding which permits code to be
refactored, tidied and optimized  is rare; this is often done ``on the sly''
in a scientifically focused grant. The UK EPSRC's ``software for the future''
call, which really permits explicit investment in software as an infrastructure,
is so oversubscribed as to have a FOUR PERCENT success rate; the demand is clear!

@@

RSEs provide a useful contribution to their Universities' *teaching* missions,
as well as for research, as they are well placed to deliver the research programming
training that many scientists now need. In the
longer term, with programming skills taught to all through their career,
we hope specialist
scientific developers will be less needed.

@@

The UKRSE community will provide initial facilities to host this list, and
continue to work to spread the initiative, but local leadership in the US
is needed if this campaign is to succeed. This will require an initial gathering
of identified research software organizations in the US to this end.

>>>>

In addition to the points noted in the main discussion (\S\ref{RSE}), we also
discussed the following:

@@

However this area develops, the need for funding to secure software as a
cyberinfrastructure component is clear. Funding which permits code to be
refactored, tidied and optimized  is rare; this is often done ``on the sly''
in a scientifically focused grant. The UK EPSRC's ``software for the future''
call, which really permits explicit investment in software as an infrastructure,
is so oversubscribed as to have a 4\% success rate; the demand is clear!

@@

RSEs provide a useful contribution to their Universities' \textbf{teaching} missions,
as well as for research, as they are well placed to deliver the research programming
training that many scientists now need. In the
longer term, with programming skills taught to all through their career,
we hope specialist
scientific developers will be less needed.

@@

The UK RSE community will provide initial facilities to host this list, and
continue to work to spread the initiative, but local leadership in the US
is needed if this campaign is to succeed. This will require an initial gathering
of identified research software organizations in the US to this end.

### 2015-11-10 WSSSPE3/report/wg_main_funding_spec_expert.tex
a few more small changes

Measures of impact and success for research programming groups, as well as for individual research software engineers, will
be required in order to make the case to the University for continued funding. Research software engineers will not be measured by publications, we hope, but by other measures. (what measures?) Middle-author publications are common for RSEs. Most RSEs welcome co-authorship on papers where the PIs consider the contribution deserves it.
(these last two statements seem contradictory, not sure which message is to be used?)

@@

We finally noted that the institutional case for such groups is made easier by having successful examples to point to. In the
UK, a collective effort to identify the research software engineering community, with individuals clearly stating "I'm a research software engineer", has been important to the campaign. It will be useful to the global effort to similarly identify emerging research software organizations, and also, importantly, to identify longer-running research software groups, which have in some cases had a long running \emph{sui-generis} existence, but which now can be identified as part of a wider solution. There remains the problem of how to "sell" the value of this investment to investigators within the university. This is an issue best addressed by the individual organizations that embark on the plan.

>>>>

Measures of impact and success for research programming groups, as well as for individual research software engineers, will
be required in order to make the case to the University for continued funding. Research software engineers will not be measured by publications, we hope, but by other measures. \todo{what measures?} Middle-author publications are common for RSEs. Most RSEs welcome co-authorship on papers where the PIs consider the contribution deserves it.
(these last two statements seem contradictory, not sure which message is to be used?)

@@

We finally noted that the institutional case for such groups is made easier by having successful examples to point to. In the
UK, a collective effort to identify the research software engineering community, with individuals clearly stating ``I'm a research software engineer,'' has been important to the campaign. It will be useful to the global effort to similarly identify emerging research software organizations, and also, importantly, to identify longer-running research software groups, which have in some cases had a long running \emph{sui-generis} existence, but which now can be identified as part of a wider solution. There remains the problem of how to "sell" the value of this investment to investigators within the university. This is an issue best addressed by the individual organizations that embark on the plan.
